% \bibitem{label}
% Text of bibliographic item

% notes:
% \bibitem{label} \note

% subbibitems:
% \begin{subbibitems}{label}
% \bibitem{label1}
% \bibitem{label2}
% If there is a note, it should come last:
% \bibitem{label3} \note
% \end{subbibitems}

%\bibitem{pixeldose}
%Maybe a TDR has the estimate of dose/yr at r=3cm.  CMS upgrade TDR says ~300 Mrad for 10 yrs of HL-LHC

\bibitem{CERN}
CERN, the European Organization for Nuclear Research, CH-1211 Geneva 23, Switzerland;
http://home.web.cern.ch

\bibitem{Bonacini}
S. Bonacini, et al., ``Characterization of a commercial 65 nm CMOS technology for SLHC applications,''
2012 JINST {\bf 7} P01015

\bibitem{RD53}
J. Christiansen, et al., ``RD Collaboration Proposal: Development of pixel readout integrated circuits for extreme rate and radiation,''
CERN-LHCC-2013-008; LHCC-P-006.
Available at http://rd53.web.cern.ch/RD53/.

\bibitem{CPPM}
M Barbero and M. Menoui, private communication.
%RD53 WG1 meetings, or private communication (M. Barbero and M. Menoui).

\bibitem{GIF}
http://www.sandia.gov/research/facilities/gamma\underline{ }irradiation\underline{ }facility.html.

\bibitem{Sandia}
Sandia National Laboratories, P.O. Box 5800, Albuquerque, NM 87185

\bibitem{TSMC}
TSMC Corporate Headquarters, 8, Li-Hsin Rd. 6, Hsinchu Science Park, Hsinchu 300-78, Taiwan, R.O.C.; telephone: +866-3-5636688;
http://www.tsmc.com

\bibitem{MOSIS}
MOSIS, 4676 Admiralty Way, 7th floor, Marina del Rey, CA  90292; telephone: +1-310-448-9400;
http://www.mosis.com

\bibitem{SB}
Sandro Bonacini, private communication.

\bibitem{Keithley}
Keithley, 28775 Aurora Road, Cleveland, Ohio 44139; telephone: +1-440-248-0400

\bibitem{K237}
A data sheet for the Keithley 237 is available at
http://www.keithley.com/data?asset=5512

\bibitem{Labview}
http://www.ni.com/labview/

\bibitem{GPIB}
A history of GPIB and IEEE-488 is available at http://www.ni.com/white-paper/3419/en/pdf

\bibitem{NI}
National Instruments, 11500 N. Mopac Expressway, Austin TX 78759; telephone: +1-877-387-0015

\bibitem{6501}
A data sheet for the NI USB-6501 is available at
http://www.ni.com/datasheet/pdf/en/ds-135

\bibitem{pdg}
K.A. Olive, et al. (Particle Data Group), Chin. Phys. C, 38, 090001 (2014), page 466
% Section 36, "Commonly used radioactive sources"

\bibitem{vortex}
Vortec 106-4-H vortex tubes were purchased from Vortec (www.vortec.com), part of the ITW Air Management business unit of Illinois Tool Works.

\bibitem{Fluke52}
Fluke Corporation, 6920 Seaway Boulevard, Everett, WA 98206; telephone: +1-425 347-6100
Specifications for the Fluke 52 digital thermometer are available at http://en-us.fluke.com/products/thermometers/fluke-52-ii-thermometer.html$\#$techspecs

\bibitem{typeK}
``Manual on the Use of Thermocouples in Temperature Measurement: 4th Edition,'' ASTM International, West Conshohocken, PA, 2014 (1993).

\bibitem{ASTM standard F1892}
ASTM Standard F1892-12, 2012, ``Standard Guide for Ionizing Radiation (Total Dose) Effects Testing of Semiconductor Devices," ASTM International, West Conshohocken, PA, 2014,DOI:10.1520/F1892-12, http://www.astm.org.

\bibitem{Schroder}
Dieter K. Schroder, \emph{Semiconductor Material and Device Characterization},
John Wiley and Sons, Inc., New York 1998.


